Playing with PCAs

### 2024-03-15 3-reports/playing_with_pcas.Rmd
pc_region_transect

>>>>

pc_region_transect %>% 
  filter(transect != "transition") %>% 
  mutate(variable = fct_reorder(variable, abs(PC1))) %>% 
  ggplot(aes(x = abs(PC1), y = variable, color = transect))+
  geom_point(size = 5)+
  scale_colour_manual(values = c("red", "blue"))+
 # xlim(0, 0.4)+
  #geom_vline(xintercept = 0)+
  labs(y = "",
       x = "|PC1|")+
  facet_grid(. ~ region)+
  theme_kp()+
  geom_vline(xintercept = 0.3, linetype = "dashed")+
  geom_vline(xintercept = 0.1, linetype = "dashed")
